\section*{References}

\begin{thebibliography}{00}

\bibitem{blood_component_1} D. Basu and R. Kulkarni, ``Overview of blood components and their preparation,'' {\it Indian J. Anaesth.}, vol. 58, no. 5, pp. 529--537, Sep.--Oct. 2014, doi: 10.4103/0019-5049.144647.
\bibitem{blood_component_2} K. L. Scott, J. Lecak, and J. P. Acker, ``Biopreservation of red blood cells: Past, present, and future,'' {\it Transfus. Med. Rev.}, vol. 19, no. 2, pp. 127--142, Apr. 2005.
\bibitem{automation_1} A. C. McQuillan and S. D. Sales, ``Designing an automated blood fractionation system,'' {\it Int. J. Epidemiol.}, vol. 37, no. suppl\_1, pp. i51--i55, Apr. 2008, doi: 10.1093/ije/dym286.
\bibitem{automation_2} N. Comasòlivas, A. Bejarano-Romero, and M. C. Cárdenas-Castiblanco, ``MT17 assessment of the productivity features and analysis of the quality parameters from the control units processed using a semi-automated, buffy coat method, in a Colombian blood bank center,'' {\it Value Health}, vol. 26, no. 6, pp. S300, Jun. 2023.
\bibitem{manual_prob_1} J. C. Boyd, R. A. Felder, K. M. Ward-Cook, C. A. Lehmann, L. E. Schoeff, and R. H. Williams, ``Preanalytical automation in the clinical laboratory,'' {\it Clinical Diagnostic Technology: The Total Testing Process}, vol. 1, pp. 107--129, 2003.
\bibitem{manual_prob_2} S. C. Gupte, ``Automation in blood centre: its impact on blood safety,'' {\it Asian J. Transfus. Sci.}, vol. 9, no. Suppl 1, pp. S6--10, Apr. 2015.
\bibitem{diff_1} ``Method and apparatus for buffy coat imaging,'' U.S. Patent 11 386 551 B2, Jul. 12, 2022.
\bibitem{diff_2} W. Mai, W. He, R. Mo, G. Liu, J. Hong, W. Li, L. Luo, and Z. Chen, ``Efficient quality control of platelet-rich plasma preparation using computer vision and deep learning,'' {\it J. Biomed. Opt.}, vol. 30, no. 6, Jun. 2025, Art. no. 065003.
\bibitem{diff_3} I. J. Bontekoe, P. F. Van der Meer, G. Mast, and D. de Korte, ``Separation of centrifuged whole blood and pooled buffy coats using the new CompoMat G5: 3 years experience,'' {\it Vox Sang.}, vol. 107, no. 2, pp. 140--147, Aug. 2014.
\bibitem{blue_1} M. L. Balter, J. M. Leipheimer, A. I. Chen, A. Shrirao, T. J. Maguire, and M. L. Yarmush, ``Automated end-to-end blood testing at the point-of-care: Integration of robotic phlebotomy with downstream sample processing,'' {\it Technology}, vol. 6, no. 2, pp. 59--66, Jun. 2018.
\bibitem{blue_2} P. Ledwig, M. Sghayyer, J. Kurtzberg, and F. E. Robles, ``Dual-wavelength oblique back-illumination microscopy for the non-invasive imaging and quantification of blood in collection and storage bags,'' {\it Biomed. Opt. Express}, vol. 9, no. 6, pp. 2743--2754, May 2018.
\bibitem{blue_3} Y. M. Serebrennikova, D. E. Huffman, and L. H. Garcia-Rubio, ``Characterization of red blood cells with multiwavelength transmission spectroscopy,'' {\it BioMed Res. Int.}, vol. 2015, 2015, Art. no. 382641.
\bibitem{blue_4} A. Hatami and M. Saadatmand, ``Extremely precise blood–plasma separation from whole blood on a centrifugal microfluidic disk (lab-on-a-disk) using separator gel,'' {\it Diagnostics}, vol. 12, no. 11, Nov. 2022, Art. no. 2873.
\bibitem{diff_cross_1} X. Shen, L. Xu, Q. Zhang, and J. Jia, ``Multi-modal and multi-spectral registration for natural images,'' in {\it Proc. Eur. Conf. Comput. Vis.}, Cham, Switzerland: Springer, Sep. 2014, pp. 309--324.
\bibitem{diff_cross_2} D. Wang, J. Liu, L. Ma, R. Liu, and X. Fan, ``Improving misaligned multi-modality image fusion with one-stage progressive dense registration,'' {\it IEEE Trans. Circuits Syst. Video Technol.}, vol. 34, no. 11, pp. 10944--10958, Jun. 2024.
\bibitem{onedim} D. S. Bacea, V. von Einem, and J. Srinivasan, ``Deep learning object detection for tracing the plasma portion of whole blood from images of medical sample containers,'' in {\it Proc. IEEE 19th Int. Conf. Intell. Comput. Commun. Process. (ICCP)}, Oct. 2023, pp. 237--244.
\bibitem{ResNet} C. Yang, D. Li, D. Sun, S. Zhang, P. Zhang, Y. Xiong, M. Zhao, T. Qi, B. Situ, and L. Zheng, ``A deep learning-based system for assessment of serum quality using sample images,'' {\it Clin. Chim. Acta}, vol. 531, pp. 254--260, Jun. 2022.
\bibitem{micformer} X. Fan, L. Liu, and H. Zhang, ``Multimodal information interaction for medical image segmentation,'' arXiv preprint arXiv:2404.16371, Apr. 2024.
\bibitem{a2f} Z. Wang and Y. Hong, ``A2FSeg: Adaptive multi-modal fusion network for medical image segmentation,'' in {\it Proc. Int. Conf. Med. Image Comput. Comput.-Assist. Interv. (MICCAI)}, Cham, Switzerland: Springer, Oct. 2023, pp. 673--681.
\bibitem{crossmodal_1} C. Doersch, A. Gupta, and A. Zisserman, ``Crosstransformers: Spatially-aware few-shot transfer,'' in {\it Adv. Neural Inf. Process. Syst.}, vol. 33, 2020, pp. 21981--21993.
\bibitem{crossmodal_2} L. Ye, M. Rochan, Z. Liu, and Y. Wang, ``Cross-modal self-attention network for referring image segmentation,'' in {\it Proc. IEEE/CVF Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2019, pp. 10502--10511.
\bibitem{phantom} S. Mukherjee, C. Beard, and Z. Li, ``MODIPHY: Multimodal obscured detection for IoT using phantom convolution-enabled faster YOLO,'' in {\it Proc. IEEE Int. Conf. Image Process. (ICIP)}, Oct. 2024, pp. 2613--2619.
\bibitem{maf} Y. Xue, Z. Ju, Y. Li, and W. Zhang, ``MAF-YOLO: Multi-modal attention fusion based YOLO for pedestrian detection,'' {\it Infrared Phys. Technol.}, vol. 118, Nov. 2021, Art. no. 103906.
\bibitem{yolo11} R. Khanam and M. Hussain, ``YOLOv11: An overview of the key architectural enhancements,'' arXiv preprint arXiv:2410.17725, Oct. 2024.
\bibitem{rs} D. S. Dawoud and P. Dawoud, {\it Serial Communication Protocols and Standards}. Denmark: River Publishers, Sep. 2022.
\bibitem{yolo8-11} P. Hidayatullah, N. Syakrani, M. R. Sholahuddin, T. Gelar, and R. Tubagus, ``YOLOv8 to YOLO11: A comprehensive architecture in-depth comparative review,'' arXiv preprint arXiv:2501.13400, Jan. 2025.
\bibitem{yolo12} N. Jegham, C. Y. Koh, M. Abdelatti, and A. Hendawi, ``YOLO evolution: A comprehensive benchmark and architectural review of YOLOv12, YOLO11, and their previous versions,'' arXiv preprint arXiv:2411.00201, Oct. 2024.
\bibitem{pyramid} T. Y. Lin, P. Dollár, R. Girshick, K. He, B. Hariharan, and S. Belongie, ``Feature pyramid networks for object detection,'' in {\it Proc. IEEE Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2017, pp. 2117--2125.
\bibitem{attention} A. Vaswani, N. Shazeer, N. Parmar, J. Uszkoreit, L. Jones, A. N. Gomez, Ł. Kaiser, and I. Polosukhin, ``Attention is all you need,'' in {\it Adv. Neural Inf. Process. Syst.}, vol. 30, 2017.
\bibitem{dualattention} M. Ding, B. Xiao, N. Codella, P. Luo, J. Wang, and L. Yuan, ``DaViT: Dual attention vision transformers,'' in {\it Proc. Eur. Conf. Comput. Vis. (ECCV)}, Cham, Switzerland: Springer, Oct. 2022, pp. 74--92.
\bibitem{spatial} P. Wu, W. Zhai, Y. Cao, J. Luo, and Z. J. Zha, ``Spatial-aware token for weakly supervised object localization,'' in {\it Proc. IEEE/CVF Int. Conf. Comput. Vis. (ICCV)}, 2023, pp. 1844--1854.
\bibitem{slide} X. Pan, T. Ye, Z. Xia, S. Song, and G. Huang, ``Slide-Transformer: Hierarchical vision transformer with local self-attention,'' in {\it Proc. IEEE/CVF Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2023, pp. 2082--2091.
\bibitem{region} R. Chen, R. Panda, and Q. Fan, ``Regional-to-local attention for vision transformers,'' U.S. Patent 11 915 474, Feb. 27, 2024.
\bibitem{concat_1} S. E. Viswanath, P. Tiwari, G. Lee, and A. Madabhushi, ``Dimensionality reduction-based fusion approaches for imaging and non-imaging biomedical data: Concepts workflow and use-cases,'' {\it BMC Med. Imag.}, vol. 17, no. 1, 2017, Art. no. 1.
\bibitem{concat_2} J. Zhao, Y. Wang, Y. Cao, M. Guo, X. Huang, R. Zhang, X. Dou, X. Niu, Y. Cui, and J. Wang, ``The fusion strategy of 2D and 3D information based on deep learning: A review,'' {\it Remote Sens.}, vol. 13, no. 20, Oct. 2021, Art. no. 4029.
\bibitem{iou_1} H. Rezatofighi, N. Tsoi, J. Gwak, A. Sadeghian, I. Reid, and S. Savarese, ``Generalized intersection over union: A metric and a loss for bounding box regression,'' in {\it Proc. IEEE/CVF Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2019, pp. 658--666.
\bibitem{iou_2} M. A. Rahman and Y. Wang, ``Optimizing intersection-over-union in deep neural networks for image segmentation,'' in {\it Proc. Int. Symp. Vis. Comput. (ISVC)}, Cham, Switzerland: Springer, Dec. 2016, pp. 234--244.
\bibitem{map_1} B. Wang, ``A parallel implementation of computing mean average precision,'' arXiv preprint arXiv:2206.09504, Jun. 2022.
\bibitem{map_2} M. Zhu, ``Recall, precision and average precision,'' Dept. Statistics and Actuarial Science, Univ. Waterloo, Waterloo, ON, Canada, Tech. Rep., Aug. 2004.

\end{thebibliography}